Active-contours driven registration method for structure-informed segmentation of diffusion MR images

### 2015-04-16 Publications/2015-NeuroImage/04-methods.tex
fixed typos, fixed reference

\begin{figure*}
\includegraphics[width=\linewidth]{figure02}
\caption{The evaluation of \regseg{} on phantom data is performed with the presented instrumental workflow:
  1) The reference surfaces $\gammaset_R$ are triangularized meshes extracted from the four binary shapes (``box'', ``ball'', ``L'', ``gyrus'');
  2) A ground-truth displacement field is generated as described in \autoref{sec:digital_phantoms}, and applied to warp
      $\gammaset_R$, obtaining $\gammaset_\text{true}$;
  3) Once warped, $\gammaset_\text{true}$ are projected to the corresponding discrete 3D volume, and downsampled creating partial volume effects to two resolutions
     of \isores[mm]{2.0} and \isores[mm]{1.0}, producing sets of tissue fractions maps;
  4) The tissue fractions are fed to an \acrfull*{mr} simulator, generating \acrfull*{t1} and \acrfull*{t2} -like images at the
     two available resolutions;
  5) The \regseg{} is run, using the warped test images as moving multispectral-image and $\gammaset_R$ as shape-priors;
  6) Assessment of the agreement between the surfaces fitted with \regseg{} ($\hat{\gammaset}_{test}$) and $\gammaset_\text{true}$
     with automatically generated visual reports and computing the Hausdorff distance between corresponding surfaces.}\label{fig:evphantoms}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics[width=\linewidth]{figure02}
\caption{The evaluation of \regseg{} on phantom data is performed with the presented instrumental workflow:
  1) The reference surfaces $\gammaset_R$ are triangularized meshes extracted from the four binary shapes (``box'', ``ball'', ``L'', ``gyrus'');
  2) A ground-truth displacement field is generated as described in \autoref{sec:digital_phantoms}, and applied to warp
      $\gammaset_R$, obtaining $\gammaset_\text{true}$;
  3) Once warped, $\gammaset_\text{true}$ are projected to the corresponding discrete 3D volume, and downsampled creating partial volume effects to two resolutions
     of \isores[mm]{2.0} and \isores[mm]{1.0}, producing sets of tissue fractions maps;
  4) The tissue fractions are fed to an \acrfull*{mr} simulator, generating \acrfull*{t1} and \acrfull*{t2} -like images at the
     two available resolutions;
  5) The \regseg{} is run, using the warped test images as multispectral moving-image and $\gammaset_R$ as shape-priors;
  6) Assessment of the agreement between the surfaces fitted with \regseg{} ($\hat{\gammaset}_{test}$) and $\gammaset_\text{true}$
     with automatically generated visual reports and computing the Hausdorff distance between corresponding surfaces.}\label{fig:evphantoms}
\end{figure*}

### 2015-04-16 Publications/2015-NeuroImage/05-results.tex
fixed typos, fixed reference

\begin{table}
		\centering
		\footnotesize
    \tabcolsep=0.1cm
    \begin{tabular}{lccccc}
    Res.   & ``gyrus'' & ``ball''  & ``box''   & ``L''     & Aggreg.    \\\hline
    1.0mm  & 0.18-0.38 & 0.31-0.45 & 0.34-0.42 & 0.34-0.40 & 0.34-0.38  \\
    2.0mm  & 0.59-0.60 & 0.65-0.76 & 0.68-0.71 & 0.67-0.77 & 0.64-0.66  \\
    \hline
    \end{tabular}
    \caption{The vertex-wise Haussdorf distance between the ground-truth surfaces and their
    corresponding estimation with \regseg{} presented distributions with 95\% CI below
    the half-voxel size in all the phantom types.
    CIs were computed using bootstrapping of 10$^4$ samples, and median as location statistic.}\label{tab:ci_phantom}
\end{table}

>>>>

\begin{table}
		\centering
		\footnotesize
    \tabcolsep=0.1cm
    \begin{tabular}{lccccc}
    Res.   & ``gyrus'' & ``ball''  & ``box''   & ``L''     & Aggreg.    \\\hline
    1.0mm  & 0.18-0.38 & 0.31-0.45 & 0.34-0.42 & 0.34-0.40 & 0.34-0.38  \\
    2.0mm  & 0.59-0.60 & 0.65-0.76 & 0.68-0.71 & 0.67-0.77 & 0.64-0.66  \\
    \hline
    \end{tabular}
    \caption{The vertex-wise Hausdorff distance between the ground-truth surfaces and their
    corresponding estimation with \regseg{} presented distributions with 95\% CI below
    the half-voxel size in all the phantom types.
    CIs were computed using bootstrapping of 10$^4$ samples, and median as location statistic.}\label{tab:ci_phantom}
\end{table}
